Estimating the distribution of block sizes as a function of average transaction rates

### 2015-10-21 paper/paper.tex
Renamed sections

\section{Motivation}
As Bitcoin becomes more popular, the transaction rate increases. Since existing Bitcoin rules limit the amount of transactions per block to one MB at some point the blocks will begin filling up. Bitcoin blocks are by design distributed according a Poisson process with a rate of discovery of one block every 10 minutes. Let $\tau$ index time in minutes, and $N(\tau)$ denote the number of blocks discovered by time $\tau$. Then for $\delta > 0$, the number of blocks discovered between time $\tau$ and time $\tau + \delta$ is Poisson distributed, that is $N(\tau + \delta) - N(\tau) \sim Poi(\delta/10)$. Let $k=1,2,\dots$ denote each of the blocks, in order. Then the amount of time between blocks is exponentially distributed. Let $\tau_k$ denote the the time when block $k$ arrives. Then $\delta_k \equiv \tau_{k} - \tau_{k-1} \stackrel{iid}{\sim} Exp(1/10)$ for $k=1,2,\dots,K$, where if $x\sim Exp(\lambda)$ it has the density $p(x) = \lambda e^{-x\lambda}$ for $x>0$ and $\lambda>0$ with mean $1/\lambda$. The longer $\delta_k$ the more time for transactions to add up before being added to the block chain as part of block $k$.

@@

\section{The Model}

>>>>

\section{Verifying the variability of transaction rates}
Let $\tau$ index time in minutes, and $N(\tau)$ denote the number of blocks discovered by time $\tau$. Then for $\delta > 0$, the number of blocks discovered between time $\tau$ and time $\tau + \delta$ is Poisson distributed, that is $N(\tau + \delta) - N(\tau) \sim Poi(\delta/10)$. Let $k=1,2,\dots$ denote each of the blocks, in order. Then the amount of time between blocks is exponentially distributed. Let $\tau_k$ denote the the time when block $k$ arrives. Then $\delta_k \equiv \tau_{k} - \tau_{k-1} \stackrel{iid}{\sim} Exp(1/10)$ for $k=1,2,\dots,K$, where if $x\sim Exp(\lambda)$ it has the density $p(x) = \lambda e^{-x\lambda}$ for $x>0$ and $\lambda>0$ with mean $1/\lambda$. The longer $\delta_k$ the more time for transactions to add up before being added to the block chain as part of block $k$.

@@

\section{Modeling the distribution of block sizes}
